A Survey of Exoskeleton Control (Draft 1.1)

### 2015-09-17 paper.tex
more updates

\begin{verbatim}
- perceive what user sees, hears, feels, smells, tastes.
- superhuman perception (RF signals, UV, IR, ultrasound, ...)
- brain signals
- spinal signals (motorneuron pools)
- motor nerve signals
- muscle signals (EMG)
- instrumenting muscles: muscle force at tendons, muscle internal pressure
- sensory nerve signals
- implanted tissue markers, other implanted sensors
- tissue imaging (ultrasound, optical)
- human/exo contact force
- contact strain, deformation rate
- exo joint/IMU sensing
- train user to emit special signals (play a videogame with their body,
  hands, eyes, neural signals, muscle signals, ...)
\end{verbatim}

@@

\subsubsection{What can be measured?}

>>>>

\begin{verbatim}
- perceive what user sees, hears, feels, smells, tastes.
- superhuman perception (RF signals, UV, IR, ultrasound, ...)
- brain signals
- spinal signals (motorneuron pools)
- motor nerve signals
- muscle electrical signals (EMG)
- muscle force signals (FMG), muscle force at tendons, muscle internal pressure
- sensory nerve signals
- implanted tissue markers, other implanted sensors
- tissue imaging (ultrasound, optical)
- human/exo contact force
- contact strain, deformation rate
- exo joint/IMU sensing
- train user to emit special signals (play a videogame with their body,
  hands, eyes, neural signals, muscle signals, ...)
\end{verbatim}

@@

\subsubsection{What can be measured or estimated?}

FMG-[06913842]

Bagnellian behavior modeling.
